\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.9, top=0.8cm, bottom=0.5cm]{geometry} %% Adjusted margins for better balance
\usepackage{import}
\usepackage{enumitem}
\usepackage{amssymb}

\name{Arjun}{Juneja}



\social[linkedin]{in/arjunjuneja}
\social[github]{ImArjunJ}
\homepage{arjunjuneja.com}
\phone[mobile]{+44 7447 361 102}
\email{arjunjuneja4u@gmail.com}
\address{London, United Kingdom}

\newcommand*{\customcventry}[7][.08em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}

\begin{document}

\makecvtitle

\vspace{-14mm}

\section{Summary}
\justifying{Software engineer specializing in low-level, high-performance native applications and backend systems. Over 8 years of self-directed education in C++, Rust, and C\#/.NET along with a pre-print research paper. Expertise spanning kernel development, LLVM, reverse engineering, and embedded systems, demonstrated through a technical blog and personal electronics lab. I've consistently won multiple hackathons with low level engineering, including Junction 2025, one of the biggest hackathons in Europe.}

\vspace{-4mm}

\section{Experience}
\customcventry{July 2026 -- Sep 2026}{Information Security Engineer}{XTX Markets}{London, UK}{}{
\begin{itemize}[leftmargin=0.6cm,label=\textbullet]
    \item Incoming Summer 2026
\end{itemize}}
\vspace{1mm}
\customcventry{Sep 2025 -- Jan 2026}{Software Engineer}{Hacktron AI}{London, UK}{}{
\begin{itemize}[leftmargin=0.6cm,label=\textbullet]
    \item Worked on AI agentic graph algorithm to auto-generate callstacks via treesitter for AI pentesting reports
    \item Created authentication flow for CLI
\end{itemize}}
\vspace{1mm}
\customcventry{Jul 2023 -- Sep 2023}{Software Engineer Intern}{BP}{London, UK}{}{
\begin{itemize}[leftmargin=0.6cm,label=\textbullet]
    \item Contract extended by 2+ months for exceptional performance and stakeholder feedback
    \item Achieved 99\%+ user satisfaction on Safety \& Assurance Power Apps panel development for 500+ assurers
    \item Constructed Power BI reports leveraging custom DAX statistical regression calculations; reports are now viewed by over 50 executives containing my contributions
\end{itemize}}
\vspace{-2mm}


\section{Projects \& Publications}
\cventry{}{jcan}{}{}{}{open-source can bus diagnostic tool featuring the first-ever linux driver for vector can hardware, signal plotting, real-time bus monitor, dbc decoding, signal visualization, and multi-adapter support. c++23, dear imgui, libusb. \href{https://github.com/ImArjunJ/jcan}{\color{blue}Project}}
\cventry{}{LogiLinux}{}{}{}{Winner of LauzHack '25. We engineered full Linux support for the Logitech MX Creative Console by comprehensively reverse-engineering the proprietary HID++ communication protocols. The system features a high-performance C++ driver backend capable of functioning as a standalone library, coupled with a polished Tauri-based UI. To ensure extensibility, we architected a complete ecosystem including a custom SDK, and plugin registry to replicate the fidelity of official drivers. \href{https://github.com/logilinux/}{\color{blue}Project}}
\cventry{}{Wavelet}{}{}{}{Winner of Junction '25. We visualize EM waves via the Maxwell equations which describe radiation propogation in a specified grid, giving time-based mathematical wave-forms. This was done in Pure C++ / OpenGL with no other dependencies. To be optimized for GPU rendering, We heavily utilized compute shaders, parallelism, culling, and graphics programming principles. \href{https://github.com/ron0studios/helmholtz}{\color{blue}Project}}
\cventry{}{Chimera: .NET Runtime Process Injection}{}{}{}{Created stealth injection framework bypassing EDR/AV systems. Reverse-engineered CLR internals to execute payloads in JIT memory regions. Documented methodology in detailed technical writeup with 5,000+ views across multiple platforms \href{https://arjunjuneja.com/blog/2025/08/08/chimera}{\color{blue}Writeup}}
\cventry{}{RX-INT: Kernel-Assisted Security Tool}{}{}{}{High-performance Windows kernel driver for real-time threat detection recognizing advanced threats (VAD manipulation, module stomping) Outperformed industry tool PE-sieve in 100\% of edge-cases through efficient caching algorithms and novel methodology \href{https://arxiv.org/abs/2508.03879}{\color{blue}Research Paper}}
\cventry{}{Hyprlenia}{}{}{}{Won 3rd Place + Best Technical Project (ICHack '26). hyper-optimised sandbox for real-time 3D emergent behaviour. generate simulations convergent towards low-energy / physics principles or biological cell evolution based on customizable growth parameters. \href{https://github.com/ron0studios/hyprlenia}{\color{blue}Project}}

\vspace{-2mm}


\section{Competitions \& Certifications}
\begin{itemize}[leftmargin=0.6cm, label=\textbullet]
    \item \textbf{Meta Hacker Cup (Top 6.5\%)}: Placed 1465 / 22,494 in Round 1 of the global coding competition (Oct 2024) \href{https://www.facebook.com/codingcompetitions/hacker-cup/2024/certificate/968836085258124}{\color{blue}Certificate}
    \item \textbf{Hackathon Winner}:  \href{https://www.linkedin.com/posts/arjunjuneja_hi-again-yes-its-the-2nd-win-in-a-week-activity-7398432080323375104-Kj4x}{\color{blue}LauzHack '25} [Nov 2025], \href{https://www.linkedin.com/posts/arjunjuneja_hi-again-i-just-won-one-of-europes-biggest-activity-7395862662816952321-cJR1}{\color{blue}Junction '25} [Nov 2025], \href{https://www.linkedin.com/posts/arjunjuneja_create-a-project-that-shapes-a-secure-tomorrow-activity-7307195841843216384-GkH9}{\color{blue}SotonHack '25} [Mar 2025], JumpStart [Sep 2024], \href{https://www.linkedin.com/posts/arjunjuneja_robohack-2025-thank-you-to-southampton-activity-7304137543397048320-6XAb}{\color{blue}RoboHack '25} [Mar 2025] (2nd),\href{https://github.com/ron0studios/hyprlenia}{\color{blue}ICHack '26} [Jan 2026] (3rd), \href{https://www.linkedin.com/posts/arjunjuneja_ichack2025-hackathon-imperialcollegelondon-activity-7292643769336619009-6Dil}{\color{blue}ICHack '25} [Jan 2025] (4th)

\end{itemize}
\vspace{-6mm}

\section{Education}
\customcventry{Sep 2024 -- Jul 2027}{BSc Computer Science}{University of Southampton}{Southampton, UK}{}{Year 1 Grade: First Class}
\customcventry{Sep 2022 -- Jul 2024}{A-Levels: Mathematics, Physics, Chemistry}{Feltham College}{London, UK}{}{Grades: A*AA}
\customcventry{Sep 2017 -- Jul 2022}{GCSEs}{Reach Academy Feltham}{London, UK}{}{Grades: 999 in Physics, Chemistry, and Mathematics}
\vspace{-4mm}

\section{Technical Skills}
\cvitem{Languages}{C++, Rust, C\#, Python, TypeScript, SQL, PHP, LLVM IR}
\cvitem{Technologies}{.NET Framework, React, Node.js, Win32 API, Windows Kernel, FPGA, Linux, Git, Security, System Verilog}
\cvitem{Developer Tools}{Visual Studio, VS Code, IDA Pro, Ghidra, x64dbg, Wireshark, Google Test}
\cvitem{Data \& DevOps}{GCP, Docker, AWS, Power BI, Power Apps, DAX, Selenium, CI/CD}

\vspace*{-4mm}

\end{document}